Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Add ref for rev 2

To close the RANS equations, two different turbulence models were used: Menter's
$k$--$\omega$ SST \cite{Menter1994} and the Spalart--Allmaras (SA) one equation
model \cite{Spalart1992}. Both closures use the eddy-viscosity approach---the SA
employing a single additional scalar transport equation for an
eddy-viscosity-like quantity $\tilde{\nu}$ and the SST solving equations for the
turbulence kinetic energy $k$ and specific dissipation $\omega$. The SST model
was chosen due to its prominence in the literature for simulating separating
flows, which we assumed to be present in the current problem in the form of
dynamic stall. The SA model was shown by Ferreira et al.~\cite{Ferreira2007} to
match experimental particle image velocimetry (PIV) results for a CFT in dynamic
stall, though this was a somewhat low Reynolds number case ($Re_c \approx 6
\times 10^4$). Further justification for using the SA model for this case comes
from Crivellini and D'Alessandro \cite{Crivellini2014}, where they successfully
modeled the laminar separation bubble and subsequent boundary layer transition
to turbulence at Reynolds numbers similar to those investigated here.

>>>>

To close the RANS equations, two different turbulence models were used: Menter's
$k$--$\omega$ SST \cite{Menter1994} and the Spalart--Allmaras (SA) one equation
model \cite{Spalart1992}. Both closures use the eddy-viscosity approach---the SA
employing a single additional scalar transport equation for an
eddy-viscosity-like quantity $\tilde{\nu}$ and the SST solving equations for the
turbulence kinetic energy $k$ and specific dissipation $\omega$. The SST model
was chosen due to its prominence in the literature for simulating separating
flows, which we assumed to be present in the current problem in the form of
dynamic stall~\cite{Para2002}. The SA model was shown by Ferreira et
al.~\cite{Ferreira2007} to match experimental particle image velocimetry (PIV)
results for a CFT in dynamic stall, though this was a somewhat low Reynolds
number case ($Re_c \approx 6 \times 10^4$). Further justification for using the
SA model for this case comes from Crivellini and D'Alessandro
\cite{Crivellini2014}, where they successfully modeled the laminar separation
bubble and subsequent boundary layer transition to turbulence at Reynolds
numbers similar to those investigated here.
